Realaus objektų sukamųjų judesių perdavimas į virtualią aplinką

### 2015-01-07 KompiuterineGrafika/projektas/paper/paper.tex
added bibliography

>>>>

\bibliography{Bibliografija}
\begin{itemize}
	\item [[AAJ+01]] - \textit{Implementing a Sensor Fusion Algorithm for 3D Orientation Detection with Inertial/Magnetic Sensors}, \url{http://franciscoraulortega.com/pubs/Algo3DFusionsMems.pdf}
	\item [[SSF+11]] - \textit{A sensor fusion algorithm for an integrated angular position estimation with inertial measurement units}, \url{http://www.date-conference.com/proceedings/PAPERS/2011/DATE11/PDFFILES/IP1_06.PDF}
	\item [[MS11]] - \textit{Modeling, Design and Experimental Study for a Quadcopter System Construction}, \url{http://brage.bibsys.no/xmlui/bitstream/id/86811/uiareport.pdf}
\end{itemize}
